Compare pseqs

### 2019-05-20 comparepseqs.Rmd
x to dset
Packrat

for (key in names(rds)) {
    pseq <- import_filter_data(rds[[key]] ,excluded = c("DIAB"))
    dset <- meta.merge.alphadiversity(x) %>%
        mutate(diversities_shannon = scale(diversities_shannon))

    alphadiversity <- list(min =  calculateglm(x, modelstring = fo.alpha.min),
                           full = calculateglm(x, modelstring = fo.alpha.full))

>>>>

for (key in names(rds)) {
    pseq <- import_filter_data(rds[[key]] ,excluded = c("DIAB"))
    dset <- meta.merge.alphadiversity(dset) %>%
        mutate(diversities_shannon = scale(diversities_shannon))

    alphadiversity <- list(min =  calculateglm(dset, modelstring = fo.alpha.min),
                           full = calculateglm(dset, modelstring = fo.alpha.full))
